Fusion Moves for Correlation Clustering

### 2014-11-14 paper/egpaper_for_review.tex
fixed all changes where i knew the fix up tp parameter choise

\subsection{Parameter Choice for CC-Fusion}
Beside the choice of the proposal generator and fusion method CC-Fusion has some more parameters, which need to be set.
The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is used to generate diversity.
Fig.~\ref{fig:parameterchoice} shows an evaluation of the impact of this parameters for a single instance of knott-3d-450 averaged over several random seeds.
The runtime depends on the number of clusters in the proposal (Fig.~\ref{fig:parameterchoice} left), which controls the size of the auxiliary move problems.
The level of noise has no major impact on the runtime.
The energy of the final solution improves with finer proposals since this increase the search-space of the moves.
Although the level of noise has to be large enough to generate diverse proposals but also not to large to generate proposals with low quality.
As shown in Fig.~\ref{fig:parameterchoice} right the useful parameter set is quite large. This allows us to use the same parameters for \emph{all}
experiments. However we would like to note, that in practice we can improve the performance by adjust these parameters for the specific problem setting.
%
%
\begin{figure}[th]
\centering
\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-time2.pdf}}
\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-value2.pdf}}
\caption{Empirical evaluation of the impact of noise used for proposal generation and proposal size.
  Proposals with many segments causes longer runtime. Noise seemed not to be a critical parameter but should be selected large enough.
}
\label{fig:parameterchoice}
\end{figure}

>>>>

\subsection{Parameter Choice for CC-Fusion}
Beside the choice of the proposal generator and fusion method CC-Fusion has some more parameters, which need to be set.
The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is used to generate diversity.
Fig.~\ref{fig:parameterchoice} shows an evaluation of the impact of this parameters for a single instance of knott-3d-450 averaged over several random seeds.
The runtime depends on the number of clusters in the proposal (Fig.~\ref{fig:parameterchoice} left), which controls the size of the auxiliary move problems.
The level of noise has no major impact on the runtime.
The energy of the final solution improves with finer proposals since this increases the search space of the moves.
The level of noise has to be large enough to generate diverse proposals but not to large to generate proposals with low quality.
As shown in Fig.~\ref{fig:parameterchoice} right the useful parameter set is quite large. This allows us to use the same parameters for \emph{all}
experiments. However we would like to note, that in practice we can improve the performance by adjusting these parameters for the specific problem setting.
%
%
\begin{figure}[th]
\centering
\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-time2.pdf}}
\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-value2.pdf}}
\caption{Empirical evaluation of the impact of noise used for proposal generation and proposal size.
  Proposals with many segments cause longer runtime. Noise seemed not to be a critical parameter but should be selected large enough.
}
\label{fig:parameterchoice}
\end{figure}
